%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Development Intern} % Position
    {JDA Software} % Company
    {Bengaluru} % Location
    {Jul. 19 - Dec. 19} % Date(s)
    {
      \begin{cvitems}
        \item{Worked on a WMS installer using Java-based InstallAnywhere tool for both Linux
         and Windows systems.}
        \item{Implemented gRPC port support in both installers.
         It added the ability to run multiple instances of WMS on a single system.}
        \item{Implemented validations for silent mode of installation, making it more robust.}
        \item{Worked on migration of legacy installer code from InstallShield to InstallAnywhere.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Intern} % Position
    {Quant One Technologies} % Company
    {Kolkata} % Location
    {May. 18 - Jul. 18} % Date(s)
    {
      \begin{cvitems}
        \item {Integrated Alphalens to provide visual analysis on the predictiveness
         of stock features.}
        % \item {Provided an API to access the intermediate data generated within Alphalense
        %  to help in further analysis of stock features.}
        \item {Implemented concepts of LFE for classification to improve predictive
         model performance on stock features.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Intern} % Position
    {Quant One Technologies} % Company
    {Kolkata} % Location
    {May. 17 - Jul. 17} % Date(s)
    {
      \begin{cvitems}
        \item {Created a GUI application in Java, providing one-click
         solutions to some of the multistep processes on the AWS console.}
        \item {Automated downloading of daily dividend data using selenium
         and stock data adjustment process.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
