%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Development} % Position
    {\href{https://github.com/prashantpiyush/Bits-PS2-form-helper}{PS II - Preference Form Helper}} % Company
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item{Simplified the preference form filling process by changing the
         drag-and-drop feature to preference input thereby eliminating the need
         to rearrange 400 rows long list.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python Development} % Position
    {\href{https://github.com/prashantpiyush/cptool}{CF Tool}} % Company
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item{Developed a competitive programming helper tool to automatically parse
         a contest for sample input and output for given problems.}
        \item{It tests the written solutions against the sample input and reports
         the errors found. Supports Java and C++ languages.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Aritificial Intelligence} % Position
    {\href{https://github.com/prashantpiyush/ai-projects}{Problem Solving Agents}} % Company
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item{Created Checkers bot in python using the Min-Max algorithm enhanced with
         Alpha-Beta Pruning.}
        \item{Developed a problem-solving agent for Max-squre Match Stick problem
         and Container Stacking problem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development} % Position
    {Website backend} % Company
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item{Implemented a CMS backend in Node.js with MongoDB using microservices
         architecture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Development} % Position
    {\href{https://github.com/prashantpiyush/yai-java}{Interpreter}} % Company
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item{Implemented a tree-walk interpreter in Java
         containing features of object-oriented and functional programming.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
